\EVOSUITE at the SBST 2018 Tool Competition

### 2018-03-15 papers/sbst18/paper_sbst18.tex
Edits

Like in previous instances of the competition, we enabled the
post-processing step of test minimisation---not for efficiency
reasons, but because minimised tests are less likely to break. To
reduce the overall time of test generation we included all assertions
rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}, which is a computationally
expensive process. The use of all assertions has a negative impact on
readability, but this is not evaluated as part of the SBST contest.

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.7\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

@@

~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these relatively positive 
results---also consistent with previous years' results---to the way
\EVOSUITE handles execution environments during test generation (e.g.,
controlling the static state of the class under test, mocking
interactions with the file system, system calls like
\texttt{System.in} and \texttt{System.currentTimeMillis},
etc.)~\cite{arcuri2014automated}.

Overall, no flaky tests were generated for the vast majority of
subjects in the competition. Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) an possibly incorrect handling of enum
types; and c) global property not being reset in between
executions. Further investigation will be needed to confirm these
conjectures and act upon them.

@@

As mentioned in the previous section, \EVOSUITE uses private API
access and functional mocking% in addition to environment
% mocking
~\cite{ICST_Mocking17}. In this competition, a total of 2,766 mock
instances were created, 1,339 private fields were set and 2,409
private methods were invoked using mocked access. Some of the Java
classes most frequently used for mocking across benchmarks are
\texttt{File} (849 instances in total), \texttt{Throwable} (284),
\texttt{PrintStream} (210) and \texttt{Thread} (114). Mocking was
particularly useful for \EVOSUITE to generate tests for the FASTJSON
benchmarks, where multiple calendar systems are necessary (e.g.,
classes \texttt{HijrahDate}, \texttt{MinguoDate},
\texttt{JapaneseDate}, \texttt{ThaiBuddhistDate} were mocked 719 times
altogether).

@@

~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
(highlighted in grey in Table~\ref{table:results}). The former two
benchmarks had missing dependencies in the competition
setup~\cite{sbst18competition}, which explains why \EVOSUITE was
incapable of generating any test. For the REDISSON benchmarks, most
executions ended with a timeout; unfortunately, we have not been able
to reproduce this behaviour locally, hence we can only conjecture that
the timeouts (reported during the initialisation phase) are due to the
large number of dependency classes (>7000) that need to be loaded for
these benchmarks to start off the test generation.

>>>>

Like in previous instances of the competition, we enabled the
post-processing step of test minimisation---not for efficiency
reasons, but because minimised tests are less likely to break. To
reduce the overall time of test generation we included all assertions
rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}, which is computationally
expensive. The use of all assertions has a negative impact on
readability, but this is not evaluated as part of the SBST contest.

@@

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{0.71\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

@@

~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these relatively positive
results---also consistent with previous years' results---to the way
\EVOSUITE handles execution environments during test generation (e.g.,
controlling the static state of the class under test, mocking
interactions with the file system, system calls like
\texttt{System.in} and \texttt{System.currentTimeMillis},
etc.)~\cite{arcuri2014automated}.  \EVOSUITE provides deterministic
replacement classes for many classes with known non-determinism,
(e.g., those related to date and time), and in particular the FASTJSON
benchmarks made heavy use of these. For example, multiple calendar
systems are necessary (e.g., classes \texttt{HijrahDate},
\texttt{MinguoDate}, \texttt{JapaneseDate},
\texttt{ThaiBuddhistDate}), and \EVOSUITE instantiated its own
replacement versions of these classes 719 times altogether, thus
potentially avoiding many flaky tests. Overall, no flaky tests were
generated for the vast majority of subjects in the competition.

Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) an possibly incorrect handling of enum
types; and c) global property not being reset in between
executions.Considering that there were still remaining flaky tests, further investigation will be needed to confirm these
conjectures and act upon them.

@@

As mentioned in the previous section, \EVOSUITE uses private API
access and functional mocking% in addition to environment
% mocking
~\cite{ICST_Mocking17}. Overall, in all tests generated in this
competition, 1,339 private fields were set and 2,409
private methods were invoked using reflection, and 15,369 Mockito mock
instances were created and configured using another 9,553 statements
(e.g., using the \text{doReturn} method). Considering the 1,804,932 overall test
statements, this means that only 1.4\% of the tests were devoted to
mocking. Amongst the 331 distinct classes for which mocks were
generated at least once there are some classes for which EvoSuite can
instantiate regular objects (e.g., \texttt{List}). This suggests that
EvoSuite sometimes struggles to generate and set up complex objects
correctly, and there is potential for future improvements.

%a total of 2,766 mock
%instances were created, using mocked access. Some of the Java
%classes most frequently used for mocking across benchmarks are
%\texttt{File} (849 instances in total), \texttt{Throwable} (284),
%\texttt{PrintStream} (210) and \texttt{Thread} (114).

@@

~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
(highlighted in grey in Table~\ref{table:results}). The former two
benchmarks had missing dependencies in the competition
setup~\cite{sbst18competition}, which explains why \EVOSUITE was
incapable of generating any test: When a dependency of the class under
test is missing, then \EVOSUITE intentionally aborts with an error to
inform the user of the configuration error. While this is desirable
behavior during regular usage, arguably in the scope of the
competition \EVOSUITE could try to ignore such errors and try to
generate tests nevertheless, as it might still be possible to cover
code even with some missing dependencies.

For the REDISSON benchmarks, most
executions ended with a timeout; unfortunately, we have not been able
to reproduce this behaviour locally, hence we can only conjecture that
the timeouts (reported during the initialisation phase) are due to the
large number of dependency classes (>7000) that need to be loaded for
these benchmarks to start off the test generation.
